---
title: "Advanced Bioinformatics 2019 Assessment"
author: "M2109262"
date: '2022-04-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

```
url- https://rpubs.com/m2109262/907403

GitHub repository- https://github.com/k21137876ZacharyWhite/Advanced-Bioinformatics-2019-assessment.git

###Task_1
```{r}
sum(5:55)
```
###Task_2
```{r}
sumfun <- function(n) {sum(5:n)}
```

```{r}
sumfun(10)
```
When n=10 sumfun produces 45
```{r}
sumfun(20)
```
When n=20 sumfun produces 200
```{r}
sumfun(100)
```
When n=100 sumfun produces 5040



**sumfun() products**

Value of n | product
------- | ---------
10    |  45
20    |  200
100   |  5040







###Task_3
```{r}
fibonacci.series <- matrix( , nrow = 12, ncol = 1)
i <- 1
for(j in 1:nrow(fibonacci.series)){
    fibonacci.series[j,] <- i
    print(i)
    ifelse(j==1, 
         i <- 1,
         i <- fibonacci.series[j,] + fibonacci.series[j-1,])
  }
```

###Task_4
```{r}
library("ggplot2")


ggplot(data = mtcars, aes(x= as.factor(gear), y= mpg)) + geom_boxplot(aes(fill= as.factor(gear))) + 
  scale_x_discrete("No. of Gears") + 
  scale_y_continuous("Miles per gallon (MPG)") + 
  ggtitle(" Box plot of MPG as function of number of gears")

```

###Task-5
```{r}
y <- cars $dist; x <- cars $speed; 
model <- lm(formula = "y ~ x")
summary(model)
```
Answers to Task-5
Slope= 3.9324
Intercept= -17.579
standard errors= 6.7584,0.4155

###Task-6
```{r}
library(ggplot2) 
ggplot_1.0 <- ggplot(data = cars, aes(x= speed, y=dist)) + geom_point() + geom_smooth(method = "lm",formula = "y ~ x")
ggplot_1.1 <- ggplot_1.0 + ggtitle ("Relationship between speed and distance")+ xlab("Speed (MPH)")+ ylab("Distance (feet)")
ggplot_1.1
```

###Task-7.1
```{r}
quad.reg <- lm(dist ~ speed + I(speed^2), data=cars)
quad.reg$coefficients
```
Assigning variables

```{r}
cars$speed_ft_Sec <- (cars$speed/3600)*5280 
quad.reg2 <- lm(dist ~ 0 + speed_ft_Sec + I(speed_ft_Sec^2), data=cars)
```
conversion of miles per hour to feet per second for easier interpretation.

obtaining the results of the proportional values of distance vs  braking 

###Task-7.2
```{r}
ggplot(data = cars, aes(x = speed_ft_Sec, y = dist)) + 
  geom_point(color = "red", size = 1.0) + 
  geom_smooth(method = "lm", formula = "y ~ 0 + x + I(x^2)",  color="blue", fullrange='TRUE') +
#  geom_point(data = cars.cp$brake.dist)
  labs(
    title = "Time Taken to Break",  
    y = "Breaking Distance", 
    x = "Speed (ft/Second)") +
  theme(plot.title = element_text(hjust =  0.5))
```


Results appear reasonable as both p and r values are both significant. and logically the time taken co incides with current estimates of the average human reaction time.
